Frustration shapes multi-channel Kondo physics: a star graph perspective

### 2022-06-29 Ref Response/RefereeResponse.tex

\section{Second referee}

\point{
My main comments concern Section II-A, in which the authors define the RG procedure. Since the results of the other Sections follow from the results of this Section, I would suggest the authors expand it. Also, some of the results that come later using this technique are familiar to the experts in the field of heavy fermions, but the RG procedure may not be.}

\response{We thank the referee for raising this point. Given the present length of the work, it will be difficult for us to add substantial material devoted to explaining various features of the URG method in the main manuscript. Instead, we have improved Sec. 4 of the Supplementary Materials (which contains the detailed derivation of the URG flow equations) to cover this: a new subsection (4A) now includes a detailed discussion of the method. In addition, we have addressed within the main manuscript the specific questions that the referee has brought up in the two points immediately following this one (and which are related to the URG method). Finally, we have also pointed the readers towards a complete derivation of the URG formalism in Refs.~\cite{anirbanurg1,anirbanurg2}. We earnestly request the referee to kindly bear with us on this.}

@@

\response{ We thank the referee for seeking a clarification on this point. We used the term “non-Fermi liquid” to reflect the fact that, in the RG sense, the low energy $k−$space Hamiltonian was not purely of an $F_{kk^\prime} n_k n_{k^\prime}$ density-density type interaction term (which is characteristic of a Fermi liquid). Indeed, the off-diagonal terms in the effective Hamiltonian obtained in eq.(44) is shown to involve a dominant contribution corresponding to an effective Marginal Fermi liquid effective Hamiltonian (eq.(49), involving a $n_{k\sigma} n_{k^{\prime}\uparrow}(1-n_{k^{\prime}\downarrow})$ interaction term, and as shown in an earlier work by us on the 2D Hubbard model~\cite{anirbanmott1,anirbanmott2,anirbanurg1,anirbanurg2}).}

\section{Third referee}

\point{
Perhaps the most interesting part is the “star graph” analysis which
are done rigorously as far as I can judge. However, I am not convinced
(especially not by the authors) that the strong coupling teaches
anything useful for the infrared physics. If there is a clear physics
lesson here, it is lost in the myriad of technicalities in the paper.
}

\response{We thank the referee for this question. Upon flowing from the weakly coupled theory to the fixed point under the renormalization group transformations, there is a reduction in the effective bandwidth of the problem (leading to reduced excitations into the conduction band) together with a growth in the effective Kondo coupling. This involves a growth in the ratio of the Kondo coupling to the bandwidth of the conduction band, and enables a study of the emergent star graph (obtained from a zero bandwidth approximation) as a ``skeletal" problem for the low-energy physics. Such an approach reveals, for instance, the ground state of the multichannel problem and the degeneracy (Sec.III of the main manuscript). Moreover, it allows studying the effects of excitations (from a calculation in the spirit of Nozieres' calculation for the single channel Kondo problem), as demonstrated by the identification of its local non-Fermi liquid nature (Sec.IV and V of the main manuscript and parts of the Supplementary Materials).
}

### 2022-06-29 manuscript/mscript_mck_full.tex
finalised sir's changes

{\color{blue}There exist other renormalisation group schemes that depend on canonical transformations, such as Wegner's continuous unitary transformations (CUT) RG (PUT IN REFERENCE) and the similarity RG method by Glaszek and Wilson (PUT IN REFERENCE). There are at least two specific distinctions between the CUT RG and the URG method adopted in the present work.
\begin{itemize}
	\item While most RG methods that apply successive unitary transformations rely on a gradual decrease in the off-diagonal content of the Hamiltonian, the URG proceeds by decoupling each discrete Fock space node at a time. In other words, the URG achieves a block-diagonalisation of the Hamiltonian at each RG step, while the CUT RG involves a gradual decay of the off-diagonal terms of the Hamiltonian in order to make it more band diagonal.
	\item The CUT RG involves choosing a truncation scheme that allows closing the RG equations. The URG, on the other hand, is able to resum the coupling expansion series through the denominator structure and the quantum fluctuation operator.  
\end{itemize}
Detailed comparisons of the URG with other methods (e.g., the functional RG, spectrum bifurcation RG etc.) can be found in Refs.~\cite{anirbanmott1,anirbanurg1}.
}

@@

The \(\chi\) is seen to diverge as \(T^{-1}\) at low temperatures.
{\color{red}Such a non-analyticity in a response function is a signature of the critical nature of the Hamiltonian.
This is in contrast to the behaviour in the non-critical exactly-screened fixed point where the ground state is unique.
There, the susceptibility becomes constant at low temperatures: \(\chi(T\to 0) = \frac{W}{4 T_K}\), \(T_K\) being the single-channel Kondo temperature and \(W\) the Wilson number \cite{wilson1975renormalization,nozieres1974fermi,bullaNRGreview,kondo_urg}.}
We have checked the case of general spin-\(S_{d}\) impurity (fig.~\ref{fig:suseptibility_impurity}) by {\color{blue}numerically diagonalising the star graph Hamiltonian}, and the general conclusion is that all exactly-screened models show a constant impurity susceptibility at \(T \to 0\), while the over-screened and under-screened cases show a diverging impurity susceptibility in the same limit.
A similar divergence is also seen in the susceptibility of the outer spins, calculated by inserting a magnetic field purely on the outer spins.

>>>>

{\color{blue}There exist other renormalisation group schemes that depend on canonical transformations, such as Wegner's continuous unitary transformations (CUT) RG~\cite{wegner1994flow} and the similarity RG method by Glazek and Wilson~\cite{glazek1993renormalization}. There are at least two specific distinctions between the CUT RG and the URG method adopted in the present work.
\begin{itemize}
	\item While most RG methods that apply successive unitary transformations rely on a gradual decrease in the off-diagonal content of the Hamiltonian, the URG proceeds by decoupling each discrete Fock space node at a time. In other words, the URG achieves a block-diagonalisation of the Hamiltonian at each RG step, while the CUT RG involves a gradual decay of the off-diagonal terms of the Hamiltonian in order to make it more band diagonal.
	\item The CUT RG involves choosing a truncation scheme that allows closing the RG equations. The URG, on the other hand, is able to resum the coupling expansion series through the denominator structure and the quantum fluctuation operator.  
\end{itemize}
Detailed comparisons of the URG with other methods (e.g., the functional RG, spectrum bifurcation RG etc.) can be found in Refs.~\cite{anirbanmott1,anirbanurg1}.
}

@@

The \(\chi\) is seen to diverge as \(T^{-1}\) at low temperatures.
Such a non-analyticity in a response function is {\color{red}a signature of the critical nature of the Hamiltonian. This is} in contrast to the behaviour in the {\color{red}non-critical} exactly-screened fixed point where the ground state is unique.
There, the susceptibility becomes constant at low temperatures: \(\chi(T\to 0) = \frac{W}{4 T_K}\), \(T_K\) being the single-channel Kondo temperature and \(W\) the Wilson number \cite{wilson1975renormalization,nozieres1974fermi,bullaNRGreview,kondo_urg}.
We have checked the case of general spin-\(S_{d}\) impurity (fig.~\ref{fig:suseptibility_impurity}) by {\color{blue}numerically diagonalising the star graph Hamiltonian}, and the general conclusion is that all exactly-screened models show a constant impurity susceptibility at \(T \to 0\), while the over-screened and under-screened cases show a diverging impurity susceptibility in the same limit.
A similar divergence is also seen in the susceptibility of the outer spins, calculated by inserting a magnetic field purely on the outer spins.
